pipeComp, a general framework for the evaluation of computational pipelines, reveals performant single-cell RNA-seq preprocessing tools

### 2020-05-04 draft.tex
Updates from Overleaf

All analyses were performed through the \href{https://github.com/plger/pipeComp}{pipeComp} Bioconductor package, which implements the pipeline framework described here. scVI results and results of the clustering section were produced with \textit{pipeComp} 0.99.4, while all other results were produced with version 0.99.2 (\textit{biorxiv}) branch of the repository). All code to reproduce the simulations and figures is available in the \url{https://github.com/markrobinsonuzh/scRNA\_pipelines\_paper} repository, which also includes the basic datasets with a standardized annotation.

>>>>

All analyses were performed through the \href{https://github.com/plger/pipeComp}{pipeComp} R package, which implements the pipeline framework described here. scVI results and results of the clustering section were produced with \textit{pipeComp} 0.99.4, while all other results were produced with version 0.99.2 (\textit{biorxiv}) branch of the repository). All code to reproduce the simulations and figures is available in the \url{https://github.com/markrobinsonuzh/scRNA\_pipelines\_paper} repository, which also includes the basic datasets with a standardized annotation.
